---
title: "Homework8"
author: "Phoebe"
date: "2023-03-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("/Users/phoebecousens/Desktop/CompBio/CousensBIOL381")
z <- read.csv("SHEAbl.csv")
```

```{r}
library(ggplot2)
library(patchwork)
library(MASS)
library(tidyverse)
library(tidyr)
```

```{r}
set <- z[,9:11]
```

```{r}
# The cross correlation(XCorr) value represents how well experimental peptide sequences fit a theoretical spectra. A unique deltaCorr different from the normal indicates that there was a post-translational modification of the peptide. 
```

```{r}
n <- 209
variance <- 2
```

`simulated data set`
```{r}
xcorr <- data.frame("xcorr",rnorm(209, mean = 2.5, sd = sqrt(variance)))
colnames(xcorr)<-c("corrtype", "corrval")
difxcorr <- data.frame("difxcorr",rnorm(209, mean = 0.5, sd = sqrt(.1)))
colnames(difxcorr)<-c("corrtype", "corrval")
uniqxcorr <- data.frame("uniqxcorr",rnorm(209, mean = 0.65, sd = sqrt(.01)))
colnames(uniqxcorr)<-c("corrtype", "corrval")

ds <- rbind(xcorr, difxcorr, uniqxcorr)
```

`null hypothesis: there is no significant difference between the xcorr values of each correlation type, indicating no post-translational modifications`

`ANOVA`

```{r}
model <- aov(corrval ~ corrtype, data = ds)
summary(model)
```

```{r}
ggplot() +
  geom_point(data = ds, aes(corrtype, corrval)) +
  geom_point(data = model, aes(corrtype,corrval), colour = "pink", size = 3) 
```

```{r}
boxplot(data=ds, corrval ~ corrtype)
```

`Determining effect size by changing mean values`

```{r}
xcorrm <- data.frame("xcorr",rnorm(209, mean = 1.1, sd = sqrt(variance)))
colnames(xcorrm)<-c("corrtype", "corrval")
difxcorrm <- data.frame("difxcorr",rnorm(209, mean = 1.0, sd = sqrt(.1)))
colnames(difxcorrm)<-c("corrtype", "corrval")
uniqxcorrm <- data.frame("uniqxcorr",rnorm(209, mean = 1.05, sd = sqrt(.01)))
colnames(uniqxcorrm)<-c("corrtype", "corrval")

dsm <- rbind(xcorrm, difxcorrm, uniqxcorrm)
```

```{r}
modelm <- aov(corrval ~ corrtype, data = dsm)
summary(modelm)
```

`By altering the means of each group to make them more equal, the significance quickly moves above the 0.05 significance level, and the data becomes insignificant. `

```{r}
ggplot() +
  geom_point(data = dsm, aes(corrtype, corrval)) +
  geom_point(data = modelm, aes(corrtype,corrval), colour = "pink", size = 3) 
```

```{r}
boxplot(data=dsm, corrval ~ corrtype)
```

`Determining sample size necessary to maintain significance`

```{r}
xcorrss <- data.frame("xcorr",rnorm(2, mean = 2.5, sd = sqrt(variance)))
colnames(xcorrss)<-c("corrtype", "corrval")
difxcorrss <- data.frame("difxcorr",rnorm(2, mean = 0.5, sd = sqrt(.1)))
colnames(difxcorrss)<-c("corrtype", "corrval")
uniqxcorrss <- data.frame("uniqxcorr",rnorm(2, mean = 0.65, sd = sqrt(.01)))
colnames(uniqxcorrss)<-c("corrtype", "corrval")

dsss <- rbind(xcorrss, difxcorrss, uniqxcorrss)
```

```{r}
modelss <- aov(corrval ~ corrtype, data = dsss)
summary(modelss)
```

`Even with a sample size of only 2, with these means and standard deviations, the significance remains below the 0.05 significance level and the data is still significant.`

```{r}
ggplot() +
  geom_point(data = dsss, aes(corrtype, corrval)) +
  geom_point(data = modelss, aes(corrtype,corrval), colour = "pink", size = 3) 
```

```{r}
boxplot(data=dsss, corrval ~ corrtype)
```
